A formal theory of digital twins

### 2023-10-24 manuscripts/xxx-2024/main.tex
work on outline

@@

@@

    \subsubsection{Product function}
    Based on product and environment state we can define the product function.
    The product function describes the logic of how the product reacts to the environment.
    This logic can be described as mapping from environment behavior to product behavior, i.e.
    \[
        F_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
    \]

    \subsubsection{Environment function}
    Similarly, we can define the environment function.
    The environment function describes the logic of how the environment reacts to the product.
    Hence, this logic can be described as mapping from product behavior to environment behavior, i.e.
    \[
        F_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
    \]

    \subsubsection{World behavior}
    Finally, based on product state and function as well as environment state and function we introduce world behavior.
    In our theory, world behavior is a combination of consistent product and environment behavior.
    We express world behavior as tuple
    \[
        B_{World} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
    \]
    such that the environment behavior $\overrightarrow{S_{Env}}$ is the result of product behavior $\overrightarrow{S_{Prod}}$, i.e.
    \[
        \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Prod}})
    \]
    and, adversely, the product behavior $\overrightarrow{S_{Prod}}$ is the result of environment behavior $\overrightarrow{S_{Env}}$, i.e.
    \[
        \overrightarrow{S_{Prod}} = F_{Prod}(\overrightarrow{S_{Env}}).
    \]

>>>>

    \subsection{TODO}
    TODO

    \subsubsection{Observer}
    TODO

    \subsubsection{Observation}
    TODO

    \subsubsection{Event}
    TODO time point and time span (observer dependent)

@@

    \subsubsection{World state}
    TODO
    \[
        S_{World} = (S_{Prod}, S_{Env}).
    \]

@@

    \subsubsection{World behavior}
    TODO
    \[
        \overrightarrow{S_{World}} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
    \]

    \subsection{TODO}
    TODO

    \subsubsection{Input}
    TODO

    \subsubsection{Output}
    TODO

    \subsubsection{Function}
    TODO

    %\subsubsection{Product function}
    %Based on product and environment state we can define the product function.
    %The product function describes the logic of how the product reacts to the environment.
    %This logic can be described as mapping from environment behavior to product behavior, i.e.
    %\[
    %    F_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
    %\]

    %\subsubsection{Environment function}
    %Similarly, we can define the environment function.
    %The environment function describes the logic of how the environment reacts to the product.
    %Hence, this logic can be described as mapping from product behavior to environment behavior, i.e.
    %\[
    %    F_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
    %\]

    %\subsubsection{World behavior}
    %Finally, based on product state and function as well as environment state and function we introduce world behavior.
    %In our theory, world behavior is a combination of consistent product and environment behavior.
    %We express world behavior as tuple
    %\[
    %    B_{World} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
    %\]
    %such that the environment behavior $\overrightarrow{S_{Env}}$ is the result of product behavior $\overrightarrow{S_{Prod}}$, i.e.
    %\[
    %    \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Prod}})
    %\]
    %and, adversely, the product behavior $\overrightarrow{S_{Prod}}$ is the result of environment behavior $\overrightarrow{S_{Env}}$, i.e.
    %\[
    %    \overrightarrow{S_{Prod}} = F_{Prod}(\overrightarrow{S_{Env}}).
    %\]
